On the adhesivity of EGGS

### 2025-02-24 calco/main.tex
minima

We now explore some further properties of kernel pairs and their link with adhesive categories. 
These two final results appear to be original, and we add their proofs in \Cref{kpp-proof}.

@@

We open this section with the definition of hypergraphs and we will see how to label them with an algebraic signature.

>>>>

We now explore some properties of kernel pairs and their link with adhesive categories. 
The results below appear to be original, and we give their proofs in \Cref{kpp-proof}.

@@

We open this section with the definition of hypergraphs and we show how to label them with an algebraic signature.
